% b2 {{{
\begin{enumerate}
\item {\bf 2016-2019}. {\it On parental desires and reproductive and filial rights: interdisciplinary perspectives on reproductive decisions and ‘the origins’ in assisted reproduction with gamete donation, surrogacy and adoption}. {\bf Spanish Ministry of Economy and Competitiveness},  reference: CSO2015-64551-C3-1-R. {\bf  Budget: 121.000 €.} Principal Investigator: {\bf Marre Cifola, Diana}.\filbreak
\item {\bf 2017-2019}. {\it Doing Right(s): Innovative tools for professionals working with LGBT families}. {\bf Erasmus+ SPHE Project, European Union},  reference: 2017-1-IT02-KA203-037006. {\bf  Budget: 272.056 €.} Principal Investigator: {\bf Marre Cifola, Diana}.\filbreak
\item {\bf 2017-2019}. {\it Doing Right(s): Innovative tools for professionals working with LGBT families}. {\bf European Union - Erasmus+ SPHE.},  reference: 2017-1-IT02-KA203-037006. {\bf  Budget: 272.056 €.} Principal Investigator: {\bf San Román Sobrino, Beatriz; Marre Cifola, Diana}.\filbreak
\item {\bf 2017-2020}. {\it Adopciones en Chile: la construcción de narrativas sobre los orígenes y la identidad.}. {\bf Comisión Nacional de Ciencia y Tecnología de Chile (CONICYT), Gobierno de Chile},  reference: FONDECYT No.3170338. {\bf  Budget: 33.000 €.} Principal Investigator: {\bf Salvo Agoglia, Irene}.\filbreak
\item {\bf 2018-2019}. {\it Dossier d’Anàlisi de polítiques públiques sobre assetjament escolar.}. {\bf Fundació Barça},  reference: . {\bf  Budget: 4.000 €.} Principal Investigator: {\bf San Román Sobrino, Beatriz}.\filbreak
\item {\bf 2019-2020}. {\it SexAFIN-Ciudad Juárez: affective, sexual and reproductive education. Research, Action and Development.}. {\bf Fase I. Fons de Solidaritat de la UAB},  reference: FSXXXVI-FS03. {\bf  Budget: 9.983,07 €.} Principal Investigator: {\bf Marre Cifola, Diana}.\filbreak
\item {\bf 2019-2022}. {\it Bridges: Building inclusive societies: Diversifying knowledge and tackling discrimination through civil society participation in universities.}. {\bf European Union - Erasmus+ Strategic Partnership.},  reference: 2019-1-ES01-KA203-064429. {\bf  Budget: 365.605 €.} Principal Investigator: {\bf Montenegro Martinez, Marisela}.\filbreak
\item {\bf 2019-2022}. {\it Brighter Future. Developing full potential after early adversity.}. {\bf European Union - Erasmus+ SPHE.},  reference: 2019- 1- ES01- KA203-065828. {\bf  Budget: 214.247 €.} Principal Investigator: {\bf San Román Sobrino, Beatriz}.\filbreak
\item {\bf 2020-2021}. {\it SexAFIN-APS: Educación afectivo-sexual y reproductiva en las escuelas de educación primaria}. {\bf Ayuntamiento de Barcelona, Programa Justicia Global},  reference: 20S05354-001. {\bf  Budget: 19.139,38 €.} Principal Investigator: {\bf Marre Cifola, Diana}.\filbreak
\item {\bf 2020-2022}. {\it SexAFIN-Ciudad Juárez: affective, sexual and reproductive education. Research, Action and Development.}. {\bf Fase II. Fons de Solidaritat de la UAB},  reference: FSXXXVII-FS02. {\bf  Budget: 7.960 €.} Principal Investigator: {\bf Alvarez Mora, Bruna; Marre Cifola, Diana}.\filbreak
\item {\bf 2020-2022}. {\it The health care of people diagnosed with severe mental disorder in the pandemic.}. {\bf Fundació Autònoma Solidària},  reference: . {\bf  Budget: 6.748 €.} Principal Investigator: {\bf Marre Cifola, Diana}.\filbreak
\item {\bf 2020-2022}. {\it Diversity \& Childhood  (DaC). Changing social attitudes towards gender diversity in children across Europe}. {\bf European Union - JUST/2018/ACTION GRANTS},  reference: SEP-210551867. {\bf  Budget: 214.247 €.} Principal Investigator: {\bf Pujol Tarrés, Joan}.\filbreak
\item {\bf 2020-2023}. {\it Repensando la Adopción desde la Perspectiva de los NIños. Historización, transiciones y relaciones en niños, niñas y adolescentes adoptados en Chile}. {\bf Agencia Nacional de Investigación y Desarrollo (ANID), Gobierno de Chile},  reference: FONDECYT No.11200491. {\bf  Budget: 85.000 €.} Principal Investigator: {\bf Salvo Agoglia, Irene}.\filbreak
\item {\bf 2021-2022}. {\it (Re)pensando la educación sexual integral desde una perspectiva de género centrada en la infancia}. {\bf Instituto de las Mujeres},  reference: . {\bf  Budget: 30.000 €.} Principal Investigator: {\bf Malgosa Gasol, Estel}.\filbreak
\item {\bf 2021-2022}. {\it Entre el Mal-estar (in)visible y el Bien-estar (im)possible}. {\bf Instituto de las Mujeres},  reference: . {\bf  Budget: 28.218,47 €.} Principal Investigator: {\bf Mantilla Salazar, Vanessa}.\filbreak
\item {\bf 2021-2022}. {\it SexAFIN-APS: Educación afectivo-sexual y reproductiva en las escuelas de educación primaria}. {\bf Ayuntamiento de Barcelona, Programa Justicia Global},  reference: 21S04887-001. {\bf  Budget: 19.950,76 €.} Principal Investigator: {\bf Marre Cifola, Diana}.\filbreak
\item {\bf 2021-2023}. {\it Austerity and Altered Life-Courses: Socio-Political Ruptures to Family, Employment and Housing Biographies Across Europe}. {\bf UK Research and Innovation Future Leaders Fellowships Outcome},  reference: . {\bf  Budget: 1.500.000 pounds.} Principal Investigator: {\bf Marre Cifola, Diana; Hall, Sarah}.\filbreak
\item {\bf 2022-2023}. {\it Educación Integral para la prevención de violencias. Encuentro Social.}. {\bf Fons de Solidaritat de la UAB},  reference: FSXXXVII-FS39, 04. {\bf  Budget: 11.789,88 €.} Principal Investigator: {\bf Alvarez Mora, Bruna; Marre Cifola, Diana}.\filbreak
\item {\bf 2022-2023}. {\it Desplazamientos y emplazamientos forzosos de niños, niñas y bebés en España (1934‐1996) a través de adopciones irregulares}. {\bf Ministerio de la Presidencia y Relaciones con las Cortes y Memoria Democrática},  reference: 092‐MD‐2021. {\bf  Budget: 8.000 €.} Principal Investigator: {\bf Marre Cifola, Diana}.\filbreak
\item {\bf 2022-2023}. {\it SexAFIN-APS: Educación afectivo-sexual y reproductiva en las escuelas de educación primaria}. {\bf Ayuntamiento de Barcelona, Programa Justicia Global},  reference: 22S05224-001. {\bf  Budget: 20.000 €.} Principal Investigator: {\bf Marre Cifola, Diana}.\filbreak
\item {\bf 2022}. {\it Fem Memòria: Relats de desplaçaments i adopcions forçades a Espanya}. {\bf Generalitat de Catalunya},  reference: MEM220/22/000024. {\bf  Budget: 2.520 €.} Principal Investigator: {\bf Marre Cifola, Diana}.\filbreak
\end{enumerate} 
% }}}
