% a1 {{{
\begin{enumerate}
\item {\bf 2019}: Alvarez, Bruna.  Reseña: Hass, R. \& Davis-Floyd, R. (Eds). Surviving the Death of your Ex: Managing the Grief No One Talks About.. {\it Revista de Antropología Iberoamericana}, 14(1), 175-179. {\bf Index: } \filbreak
\item {\bf 2019}: Alvarez, Bruna.  Surviving the Death of your Ex: Managing the Grief No One Talks About. {\it Aibr-Revista De Antropologia Iberoamericana}, 14(1), 175-179. {\bf Index: JCR: 0.313: .  Citations: 0. } \\ DOI: 10.11156/aibr.140110. \filbreak
\item {\bf 2019}: Arreciado Marañón, A.; Rodríguez‐Martín, D.; Galbany‐Estragués, P.  Male nurses' views of gender in the nurse–family relationship in paediatric care. {\it International Nursing Review}, 66(4), 563-570. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.1111/inr.12541. \filbreak
\item {\bf 2019}: Arreciado Marañón, Antonia; Isla Pera, Mª Pilar.  Confusion About Professional Autonomy Among Final-year Nursing Students in Spain. {\it Journal of Professional Nursing: Official Journal of the American Association of Colleges of Nursing}, 35(2), 147-152. {\bf Index: PubMed. } \\ DOI: 10.1016/j.profnurs.2018.07.008. \filbreak
\item {\bf 2019}: Gaggiotti-Marre, S.; Martinez, F.; Coll, L.; Garcia, S.; Álvarez, M.; Parriego, M.; Barri, P. N.; Polyzos, N.; Coroleu, B.  Low serum progesterone the day prior to frozen embryo transfer of euploid embryos is associated with significant reduction in live birth rates. {\it Gynecological Endocrinology}, 35(5), 439-442. {\bf Index: JCR: 1.571: JCR: 1.571, Q3 Obstetrics \& Gynecology, Position 54/83;.  } \\ DOI: 10.1080/09513590.2018.1534952. \filbreak
\item {\bf 2019}: Galbany‐Estragués, Paola; Millán‐Martínez, Pere; Mar Pastor‐Bravo, María; Nelson, Sioban.  Emigration and job security: An analysis of workforce trends for Spanish‐trained nurses (2010–2015). {\it Journal of Nursing Management}, 27(6), 1224-1232. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.1111/jonm.12803. \filbreak
\item {\bf 2019}: Gandarias Goikoetxea, Itziar; Montenegro Martínez, Marisela; Pujol-Tarrés, Joan.  Interseccionalidad, identidad y articulación: hacia una política de la agregación. {\it Feminismo/s}, 33, 35-63. {\bf Index: rua.ua.es. } \\ DOI: 10.14198/fem.2019.33.02. \filbreak
\item {\bf 2019}: Herrera, Florencia; Salvo Agoglia, Irene; Navarro, Javiera.  Reproducción con terceras partes en Chile: comunicando orígenes y construyendo parentesco. {\it Política y Sociedad}, 56(3), 691-711. {\bf Index: JCR: 0.21: Q4 Political Science.  SJR 0.191 Q3 Sociology and Political Science. Citations: 1. } \\ DOI: 10.5209/poso.60536. \filbreak
\item {\bf 2019}: Herrera, Florencia; Salvo Agoglia, Irene; Navarro, Javiera.  Reproducción por terceras partes en Chile: comunicando orígenes y construyendo parentesco. {\it Política y Sociedad}, 56(3), 691-711. {\bf Index: JCR: 0.21: Q4 Political Science.  Citations: 1. } \\ DOI: 10.5209/poso.60536. \filbreak
\item {\bf 2019}: Insausti, Santiago Joaquin.  Una historia del Frente de Liberación Homosexual y la izquierda en Argentina.. {\it Revista Estudos Feministas}, 27(2), 1-17. {\bf Index: SJR 0.246 Q3 Gender Studies. Citations: 1. } \\ DOI: 10.1590/1806-9584-2019v27n254280. \filbreak
\item {\bf 2019}: Insausti, Santiago Joaquín.  ¿Hedonistas o revolucionarios? Política homosexual radical e izquierda trotskista en Argentina y Brasil (1967-1983). {\it Mora}, 25(25), 85-110. {\bf Index: SCIELO. } \\ DOI: 10.34096/mora.n25.8493. \filbreak
\item {\bf 2019}: Salvo Agoglia, Irene; Alfaro Monsalve, Karen.  'Irregular Adoptions' in Chile: New Political Narratives About The Right To Know One's Origins. {\it Children \& Society}, 33(3), 201-212. {\bf Index: JCR: 0.826: Q3 Social Work.  SJR 0.66 Q2 Education. Citations: 6. } \\ DOI: 10.1111/chso.12324. \filbreak
\item {\bf 2019}: Salvo Agoglia, Irene; Jociles-Rubio, María Isabel.  Adopciones monoparentales de niños y niñas con «necesidades especiales»: entre el déficit y el empoderamiento. {\it Papers. Revista de Sociologia}, 104(4), 661-686. {\bf Index: JCR: 0.2: SJR Q3 Social Sciences (Miscellaneous), Social and Political Science.  Citations: 2. } \\ DOI: 10.5565/rev/papers.2502. \filbreak
\item {\bf 2019}: Salvo Agoglia, Irene; San Román, Beatriz.  (Re) visitando a la madre (des)naturalizada. Búsquedas y encuentros entre personas adoptadas en Chile y sus madres de origen. {\it Revista de Estudios Sociales}, 68, 75-87. {\bf Index: JCR: 0.17: Q2 Cultural Studies.  Q3 SJR 0.742 Social Issues. } \\ DOI: 10.7440/res68.2019.07. \filbreak
\item {\bf 2019}: Vergara, Ana; Sepulveda, Mauricio; Salvo, Irene.  Being a parent and being a child in Chile today: the relational construction of subject positions in a neoliberal context. {\it Subjectivity}, 12(4), 371-388. {\bf Index: JCR: 0.79: Q2 Social Sciences Interdisciplinary.  SJR: 0.462, Q2, Social Psychology. Citations: 4. } \\ DOI: 10.1057/s41286-019-00084-7. \filbreak
\item {\bf 2020}: Cazorla-Ortiz, Gemma; Galbany-Estragués, Paola; Obregón-Gutiérrez, Noemí; Goberna-Tricas, Josefina.  Understanding the Challenges of Induction of Lactation and Relactation for Non-Gestating Spanish Mothers. {\it Journal of Human Lactation}, 36(3), 528-536. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.1177/0890334419852939. \filbreak
\item {\bf 2020}: Espejo, Beatriz; Aljama Cuenca, Patricia; Pujol Tarrés, Joan.  Articulations and controversies in sex-work trans-activism. {\it Critical Social Policy}, 40(2). {\bf Index: journals.sagepub.com. } \\ DOI: 10.1177/0261018319897042. \filbreak
\item {\bf 2020}: Gaggiotti-Marre, Sofia; Álvarez, Manuel; González-Foruria, Iñaki; Parriego, Mònica; Garcia, Sandra; Martínez, Francisca; Barri, Pedro N; Polyzos, Nikolaos P; Coroleu, Buenaventura.  Low progesterone levels on the day before natural cycle frozen embryo transfer are negatively associated with live birth rates. {\it Human Reproduction}, 35(7), 1623-1629. {\bf Index: JCR: 6.918: JCR: 6.918, Q1 Reproductive biology, Position 3/30;.  } \\ DOI: 10.1093/humrep/deaa092. \filbreak
\item {\bf 2020}: Garcia-Quiroga, Manuela; Salvo Agoglia, Irene.  Too Vulnerable to Participate? Challenges for Meaningful Participation in Research With Children in Alternative Care and Adoption. {\it International Journal of Qualitative Methods}, 19, 1609406920958965. {\bf Index: JCR: 2.767: Impact factor JCR:  2.257, Q1 Social Sciences, Interdisciplinary.  Citations: 5. } \\ DOI: 10.1177/1609406920958965. \filbreak
\item {\bf 2020}: García-Sierra, Rosa; Fernández-Cano, María Isabel; Manresa-Domínguez, Josep María; Feijoo-Cid, María; Moreno Gabriel, Eduard; Arreciado Marañón, Antonia; Ramos-Roure, Francesc; Segura-Bernal, Jordi; Torán-Monserrat, Pere.  Psychological Distress and Somatization in Immigrants in Primary Health Care Practices. {\it Healthcare (Basel, Switzerland)}, 8(4), E557. {\bf Index: PubMed. } \\ DOI: 10.3390/healthcare8040557. \filbreak
\item {\bf 2020}: Giralt Palou, Rosa; Prat Vigué, Gemma; Tort-Nasarre, Glòria.  Attitudes and stigma toward mental health in nursing students: A systematic review. {\it Perspectives in Psychiatric Care}, 56(2), 243-255. {\bf Index: SJR 0.54 Q2 Psychiatric Mental Health (2020). Citations: 1. } \\ DOI: 10.1111/ppc.12419. \filbreak
\item {\bf 2020}: González-Foruria, Iñaki; Gaggiotti-Marre, Sofia; Álvarez, Manuel; Martínez, Francisca; García, Sandra; Rodríguez, Ignacio; Coroleu, Buenaventura; Polyzos, Nikolaos P.  Factors associated with serum progesterone concentrations the day before cryopreserved embryo transfer in artificial cycles. {\it Reproductive BioMedicine Online}, 40(6), 797-804. {\bf Index: JCR: 3.282: JCR: 3.282, Q1, Obstetrics \& Gynecology, Position 17/83.  SJR: 1.208, Q1, Reproductive medicine.. Citations: 10. } \\ DOI: 10.1016/j.rbmo.2020.03.001. \filbreak
\item {\bf 2020}: Insausti, Santiago Joaquin; Fernandez, Maximo Javier.  De chongos y mayates: masculinidades y sexo heterosexual entre hombres en Argentina y México (1950-1990). {\it Historia Crítica}, 77, 133-156. {\bf Index: JCR: 1: Q1 History.  SJR 0.2 Q1 History. Citations: 0. } \\ DOI: https://doi.org/10.7440/histcrit77.2020.06. \filbreak
\item {\bf 2020}: Jociles-Rubio, Maria Isabel; Salvo Agoglia, Irene.  “Siempre le he contado su historia”: prácticas y narrativas familiares sobre “los orígenes” en adopciones monoparentales. {\it Maná, Revista de Antropología}, {\bf Index: } \filbreak
\item {\bf 2020}: Molas, Anna; Perler, Laura.  Selecting women, taming bodies? Body ontologies in egg donation practices in Spain. {\it Tapuya: Latin American Science, Technology and Society}, 3(1), 396-414. {\bf Index: SJR: 0.127 Q4 Social Sciences. } \\ DOI: https://doi.org/10.1080/25729861.2020.1781371. \filbreak
\item {\bf 2020}: Nelson, Sioban; Galbany-Estragues, Paola; Gallego-Caminero, Gloria.  The Nurses No-One Remembers: Looking for Spanish Nurses in Accounts of the Spanish Civil War (1936-1939). {\it Nursing History Review}, 28, 63-92. {\bf Index: Citations: 1. } \\ DOI: 10.1891/1062-8061.28.63. \filbreak
\item {\bf 2020}: Roca, Judith; Reguant, Mercedes; Tort, Glòria; Canet, Olga.  Developing reflective competence between simulation and clinical practice through a learning transference model: A qualitative study. {\it Nurse Education Today}, 92, 104520. {\bf Index: Citations: 3. } \\ DOI: 10.1016/j.nedt.2020.104520. \filbreak
\item {\bf 2020}: Romeu‐Labayen, Maria; Rigol Cuadra, Maria Assumpta; Galbany‐Estragués, Paola; Blanco Corbal, Serafín; Giralt Palou, Rosa Maria; Tort‐Nasarre, Glòria.  Borderline personality disorder in a community setting: service users' experiences of the therapeutic relationship with mental health nurses. {\it International Journal of Mental Health Nursing}, 29(5), 868-877. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.1111/inm.12720. \filbreak
\item {\bf 2020}: Salvo Agoglia, Irene; Marre, Diana.  Children forever: The search for origins among Chilean adults who were adopted. {\it Child \& Family Social Work}, 25(1), 127-134. {\bf Index: JCR: 1,233: Q1 Family Studies.  Q1 SJR 0.9 Health Social Science. Citations: 1. } \\ DOI: 10.1111/cfs.12666. \filbreak
\item {\bf 2020}: Sanmiquel-Molinero, Laura.  Los Estudios de la Dis/capacidad: una propuesta no individualizante para interrogar críticamente la producción del cuerpo-sujeto discapacitado. {\it Papeles del CEIC}, 2020/2(Paper 231), Papel 231. {\bf Index: 0.08 Q4 Social Issues (ESCI). Citations: 16. } \\ DOI: 10.1387/pceic.20974. \filbreak
\item {\bf 2020}: Sanmiquel-Molinero, Laura; Pujol-Tarrés, Joan.  Putting emotions to work: the role of affective disablism and ableism in the constitution of the dis/abled subject. {\it Disability \& Society}, 35(4), 542-569. {\bf Index: JCR: 3.3: Q1 Social Sciences - Interdisciplinary.  SJR 0.852 Q1 Health (social science). Citations: 26. } \\ DOI: 10.1080/09687599.2019.1650719. \filbreak
\item {\bf 2020}: Vergara del Solar, Ana; Sepulveda Galeas, Mauricio; Salvo Agoglia, Irene.  Parents' economic efforts in the discourses of Chilean children: ethical reflexivity and reciprocal care. {\it Families Relationships and Societies}, 9(1), 59-74. {\bf Index: JCR: 0.759: Q4 Family Studies.  SJR: 0.43 Q2 Sociology and Political Sciences. Citations: 0. } \\ DOI: 10.1332/204674319X15645389004469. \filbreak
\item {\bf 2020}: Álvarez Martínez-Conde, Catalina; Montenegro Martínez, Marisela.  Memoria, Migración y Acción colectiva: Luchas migrantes en Barcelona. {\it Scripta Nova. Revista Electrónica de Geografía y Ciencias Sociales}, 24(0), Art. 646. {\bf Index: revistes.ub.edu. } \\ DOI: 10.1344/sn2020.24.28407. \filbreak
\item {\bf 2020}: Álvarez Martínez-Conde, Catalina; Romero Boteman, Clara Elena; Fulladosa Leal, Karina; Montenegro Martínez, Marisela.  Memories of the struggles for the rights of immigrant women in Barcelona. {\it Critical Social Policy}, 40(2), 215-233. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.1177/0261018319895499. \filbreak
\item {\bf 2021}: .  Special Issue: Irregularities in Transnational Adoptions and Child Appropriations: Challenges for Reparation Practices. {\it Childhood. A Journal of Global Child Research}, {\bf Index: } \filbreak
\item {\bf 2021}: Alvarez, Bruna.  Review: Sexualities, Gender and Violence. A view from the Iberian Peninsula. {\it Quaderns}, 37(1), 189-192. {\bf Index: } \filbreak
\item {\bf 2021}: Ben, Pablo; Joaquín Insausti, Santiago.  Historical trends leading to the same-sex marriage law in Argentina. {\it Cahiers des Amériques latines}, 98, 153-169. {\bf Index: journals.openedition.org. } \\ DOI: 10.4000/cal.14174. \filbreak
\item {\bf 2021}: Comeila, Agusti; Casas-Baroy, Joan-Caries; Comella-Company, Anna; Galbany-Estragues, Paola; Pujol, Ramon; Marc-Amengual, Jaume-Miquel.  Burnout and academic performance: effect of the combination of remunerated jobs and starting university degree studies. {\it Retos-Nuevas Tendencias En Educacion Fisica Deporte Y Recreacion}, 41, 844-853. {\bf Index: 0.25 Q4 Hospitality, Leisure, Sport \& Tourism (ESCI). Citations: 0. } \filbreak
\item {\bf 2021}: Fonseca, Claudia; Marre, Diana; Rifiotis, Fernanda.  Número especial Governança reprodutiva. {\it Horizontes Antropológicos}, 61, 7-46. {\bf Index: SJR 0.36 Q2 Anthropology. Citations: 0. } \filbreak
\item {\bf 2021}: Fonseca, Claudia; Marre, Diana; Rifiotis, Fernanda.  Governança reprodutiva: um assunto de suma relevância política. {\it Horizontes Antropológicos}, 61, 7-46. {\bf Index: Citations: 0. } \filbreak
\item {\bf 2021}: Fuentes-Pumarola, Concepcio; Reyes-Amargant, Zaira; Berenguer-Simon, Alba; Ballester-Ferrando, David; Burjales-Marti, Maria Dolors; Rigol-Cuadra, Assumpta; Maestre-Gonzalez, Elena; Rascon-Hernan, Carolina; Galbany-Estragues, Paola; Rodriguez-Martin, Dolors.  Alcohol Use and Sexual Violence among Nursing Students in Catalonia, Spain: A Multicentre Cross-Sectional Study. {\it International Journal of Environmental Research and Public Health}, 18(11), 6036. {\bf Index: JCR: 3.39: .  Citations: 1. } \\ DOI: 10.3390/ijerph18116036. \filbreak
\item {\bf 2021}: Galbany-Estragués, Paola; Glòria, Gloria Tort-Nasarré,; Romeu-Labayen, Maria, Martí; Alvarez, Bruna; Subías-Miquel, Martí; Vázquez-Segura, Eva; Marre, Diana.  Front‐line nurses’ responses to organizational changes during the COVID‐19 in Spain. A qualitative rapid appraisal. {\it Journal of Nursing Management}, 29(7), 1983-1991. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.1111/jonm.13362. \filbreak
\item {\bf 2021}: Gallego Molinero, Aranzazu; Clemente-Martínez, Chandra Kala.  Irregularities in transnational adoptions and child appropriations: Challenges for reparation practices. {\it Childhood}, 28(4), 467-476. {\bf Index: JCR: 2.864: Impact factor JCR: 2.864, Q1.  SJR Q2 0.966 Developmental and Educational Psychology. Citations: 0. } \\ DOI: 10.1177/09075682211066379. \filbreak
\item {\bf 2021}: Gesteira, Soledad; Salvo Agoglia, Irene; Villalta, Carla; Alfaro Monsalve, Karen.  Child appropriations and irregular adoptions: Activism for the “right to identity,” justice, and reparation in Argentina and Chile. {\it Childhood}, 28(4), 585-599. {\bf Index: JCR: 2.864: JCR: 2.864, Q1 Social Sciences, Interdisciplinary ;.  Citations: 1. } \\ DOI: 10.1177/09075682211028648. \filbreak
\item {\bf 2021}: Giralt Palou, Rosa; Prat Vigué, Gemma; Torà Suarez, Núria; Romeu-Labayen, Maria; Tort-Nasarre, Glòria.  The development of positive attitudes toward mental health among university nursing students: Countering the role of social desirability. {\it Perspectives in Psychiatric Care}, n/a(n/a). {\bf Index: JCR: 2.186: Impact factor JCR: 2.186, Q2 Nursing;.  Citations: 0. } \\ DOI: 10.1111/ppc.12976. \filbreak
\item {\bf 2021}: Griffen, Adrienne; McIntyre, Lynne; Belsito, Jamie Zahlaway; Burkhard, Joy; Davis, Wendy; Kimmel, Mary; Stuebe, Alison; Clark, Crystal; Meltzer-Brody, Samantha.  Perinatal Mental Health Care In The United States: An Overview Of Policies And Programs: Study examines perinatal mental health care policies and programs in the United States.. {\it Health Affairs}, 40(10), 1543-1550. {\bf Index: JCR: 6.301: Q1 Health Care Sciences \& Services; Health Care Policy and Services.  SJR: 3,837, Q1 Health Policy.. Citations: 0. } \\ DOI: 10.1377/hlthaff.2021.00796. \filbreak
\item {\bf 2021}: Insausti, Santiago.  Le memorie della violenza statale contro la diversità sessuale nell’ultima dittatura militare argentina. {\it Bibliomanie. Letterature, storiografie, semiotiche}, 51(8). {\bf Index: AGENZIA NAZIONALE DI VALUTAZIONE DEL SISTEMA UNIVERSITARIO E DELLA RICERCA. } \\ DOI: 10.48276/issn.2280-8833.6814. \filbreak
\item {\bf 2021}: Marre, Diana; Gaggiotti, Hugo.  Irregular adoptions and infrastructures of memory in Spain: remnant practices from the Franco Regime. {\it Childhood}, 28(4), 570-584. {\bf Index: JCR: 2.864 (2020): Q1 Social Science Interdisciplinary (2020).  Citations: 0. } \\ DOI: 10.1177/09075682211061448. \filbreak
\item {\bf 2021}: Martinez-Morato, Sergio; Feijoo-Cid, Maria; Galbany-Estragues, Paola; Fernandez-Cano, Maria Isabel; Arreciado Maranon, Antonia.  Emotion management and stereotypes about emotions among male nurses: a qualitative study. {\it Bmc Nursing}, 20(1), 114. {\bf Index: JCR: 2.283: Q2 Nursing.  SJR: 0,91, Q1 Nursing. Citations: 0. } \\ DOI: 10.1186/s12912-021-00641-z. \filbreak
\item {\bf 2021}: Molas, Anna.  The Oocyte Economy: The Changing Meaning of Human Eggs. Catherine Walby, Durham: Duke University Press, 2019, 248 pp.. {\it Medical Anthropology Quarterly}, 35(4), 87-89. {\bf Index: JCR: 2.475: Q1 Anthropology; Q2 Public, Environmental and Occupational Health; Q2 Social Sciencies Biomedical.  SJR 0.855 Q1 Anthropology; Q2 Medicine (Miscellaneous); Q1 Visual Arts and Performing Arts. Citations: 0. } \\ DOI: 10.1111/maq.12670. \filbreak
\item {\bf 2021}: Molas, Anna; Whittaker, Andrea.  Beyond the making of altruism: branding and identity in egg donation websites in Spain. {\it BioSocieties}, {\bf Index: JCR: 2.351: Q2 Social Sciences Biomedical.  SJR 0.723 Q2 Health policy; Health (social science). Citations: 0. } \\ DOI: 10.1057/s41292-020-00218-0. \filbreak
\item {\bf 2021}: Moreno, Lina Marín; Montenegro, Marisela.  Desterradas del río. Hidroituango y la destrucción del cuerpo-territorio por megaproyectos. Entre el interés general y el sostenimiento de la vida. {\it Iberoamericana – Nordic Journal of Latin American and Caribbean Studies}, 50(1), 84–93. {\bf Index: Citations: 0. } \\ DOI: 10.16993/iberoamericana.520. \filbreak
\item {\bf 2021}: Pollina-Pocallet, Mercè; Artigues-Barberà, Eva; Tort-Nasarre, Glòria; Sol, Joaquim; Azlor, Laura; Foguet-Boreu, Quintí; Ortega-Bravo, Marta.  Self-Perception and Self-Acceptance Are Related to Unhealthy Weight Control Behaviors in Catalan Adolescents: A Cross-Sectional Study. {\it International Journal of Environmental Research and Public Health}, 18(9), 4976. {\bf Index: SJR 0.75 Q2 Health, Toxicology and Mutagenesis. Citations: 0. } \\ DOI: 10.3390/ijerph18094976. \filbreak
\item {\bf 2021}: Ramírez-March, Álvaro; Montenegro, Marisela.  “Volem Acollir”: Humanitarismo y Posiciones de Sujeto en la Articulación de la Solidaridad en Cataluña. {\it Dados}, 64(1). {\bf Index: SciELO. } \\ DOI: 10.1590/dados.2021.64.1.227. \filbreak
\item {\bf 2021}: Romeu-Labayen, Maria; Tort-Nasarre, Gloria; Alvarez, Bruna; Subias-Miquel, Marti; Vazquez-Segura, Eva; Marre, Diana; Galbany-Estragues, Paola.  Spanish nurses' experiences with personal protective equipment and perceptions of risk of contagion from COVID-19: A qualitative rapid appraisal. {\it Journal of Clinical Nursing}, {\bf Index: JCR: 3.036: Q1 Nursing.  SJR 0.94 Q2 Medicine (Miscellaneous); Q1 Nursing (Miscellaneous). Citations: 1. } \\ DOI: 10.1111/jocn.16031. \filbreak
\item {\bf 2021}: Romeu-Labayen, Maria; Tort-Nasarre, Glòria; Alvarez, Bruna; Subías-Miquel, Martí; Vázquez-Segura, Eva; Marre, Diana; Galbany-Estragués,, Paola.  Spanish nurses’ experiences with personal protective equipment and perceptions of risk of contagion from COVID-19: A qualitative rapid appraisal. {\it Journal of Clinical Nursing}, , 1-13. {\bf Index: } \\ DOI: https://doi.org/10.1111/jocn.16031. \filbreak
\item {\bf 2021}: Romeu‐Labayen, Maria; Tort‐Nasarre, Glòria; Rigol Cuadra, M. Assumpta; Giralt Palou, Rosa; Galbany‐Estragués, Paola.  The attitudes of mental health nurses that support a positive therapeutic relationship: The perspective of people diagnosed with BPD. {\it Journal of Psychiatric and Mental Health Nursing}, , jpm.12766. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.1111/jpm.12766. \filbreak
\item {\bf 2021}: Salvo Agoglia, Irene; Herrera, Florencia.  "I Assumed He Didn't Exist": The Birth Father as the Invisible Member of the Adoption Kinship Network. {\it Journal of Family Issues}, 42(5), 984-1006. {\bf Index: JCR: 2.072: Q3 Family Studies.  SJR: 0.81 Q1 Social Sciences. Citations: 2. } \\ DOI: 10.1177/0192513X20984509. \filbreak
\item {\bf 2021}: San Román, Beatriz.  ‘I prefer not to know’: Spain’s management of transnational adoption demand and signs of corruption. {\it Childhood}, 28(4), 492-508. {\bf Index: JCR: 0.97: Impact factor JCR (2020): 0.97, Q2 Social Sciences.  Citations: 0. } \\ DOI: 10.1177/09075682211064970. \filbreak
\item {\bf 2021}: Souza, Dyego L. B.; Oliveras-Fabregas, Albert; Minobes-Molina, Eduard; de Camargo Cancela, Marianna; Galbany-Estragués, Paola; Jerez-Roig, Javier.  Trends of multimorbidity in 15 European countries: a population-based study in community-dwelling adults aged 50 and over. {\it BMC Public Health}, 21(1), 76. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.1186/s12889-020-10084-x. \filbreak
\item {\bf 2021}: Tort-Nasarre, Glòria; Pollina Pocallet, Mercè; Artigues-Barberà, Eva.  The Meaning and Factors That Influence the Concept of Body Image: Systematic Review and Meta-Ethnography from the Perspectives of Adolescents. {\it International Journal of Environmental Research and Public Health}, 18(3), 1140. {\bf Index: SJR 0.75 Q2 Health, Toxicology and Mutagenesis. Citations: 4. } \\ DOI: 10.3390/ijerph18031140. \filbreak
\item {\bf 2021}: Vilafranca Cartagena, Mireia; Tort-Nasarre, Glòria; Rubinat Arnaldo, Esther.  Barriers and Facilitators for Physical Activity in Adults with Type 2 Diabetes Mellitus: A Scoping Review. {\it International Journal of Environmental Research and Public Health}, 18(10), 5359. {\bf Index: SJR 0.75 Q2 Health, Toxicology and Mutagenesis. Citations: 4. } \\ DOI: 10.3390/ijerph18105359. \filbreak
\item {\bf 2021}: Álvarez, Manuel; Gaggiotti-Marre, Sofía; Martínez, Francisca; Coll, Lluc; García, Sandra; González-Foruria, Iñaki; Rodríguez, Ignacio; Parriego, Mónica; Polyzos, Nikolaos P; Coroleu, Buenaventura.  Individualised luteal phase support in artificially prepared frozen embryo transfer cycles based on serum progesterone levels: a prospective cohort study. {\it Human Reproduction}, 36(6), 1552-1560. {\bf Index: JCR: 6.918: .  Citations: 10. } \\ DOI: 10.1093/humrep/deab031. \filbreak
\item {\bf 2022}: Alvarez, Bruna; Marre, Diana.  Motherhood in Spain: From the “Baby Boom” to “Structural Infertility”. {\it Medical Anthropology}, 41(6-7), 718-731. {\bf Index: } \\ DOI: 10.1080/01459740.2021.1961246. \filbreak
\item {\bf 2022}: De Zordo, Silvia; Marre, Diana; Smeietana, Marcin.  ‘Demographic anxieties in the age of ‘fertility decline’.. {\it Medical Anthropology}, 41(6-7), 591-599. {\bf Index: JCR: 2.189: .  } \\ DOI: 10.1080/01459740.2022.2099851. \filbreak
\item {\bf 2022}: De Zordo, Silvia; Marre, Diana; Smeietana, Marcin.  Double Special Issue: Demographic Anxieties in the Age of ‘Fertility Decline’, Medical Anthropology. {\it Medical Anthropology}, 41(6-7), 591-761. {\bf Index: } \filbreak
\item {\bf 2022}: García‐Santesmases, Andrea; Sanmiquel‐Molinero, Laura.  Embodying disabled liminality: A matter of mal/adjustment to dis/ableism. {\it Sociology of Health \& Illness}, 44(2), 377-394. {\bf Index: JCR: 3.041: Q1 Social Sciences, Biomedical.  SJR 1.146 Q1 Health Policy; Health (social science); Public Health, Environmental and Occupational Health. Citations: 10. } \\ DOI: 10.1111/1467-9566.13439. \filbreak
\item {\bf 2022}: Giralt Palou, Rosa; Prat Vigué, Gemma; Romeu-Labayen, Maria; Tort-Nasarre, Glòria.  Analysis of Stigma in Relation to Behaviour and Attitudes towards Mental Health as Influenced by Social Desirability in Nursing Students. {\it International Journal of Environmental Research and Public Health}, 19(6), 3213. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.3390/ijerph19063213. \filbreak
\item {\bf 2022}: Insausti, Santiago Joaquín.  De asesinos a víctimas: homosexualidad masculina y crimen en la prensa argentina (1945-1989). {\it Revista Paginas}, 14(34). {\bf Index: SJR 0.19 Q1 History. } \\ DOI: 10.35305/rp.v14i34.590. \filbreak
\item {\bf 2022}: March-Amengual, Jaume-Miquel; Cambra Badii, Irene; Casas-Baroy, Joan-Carles; Altarriba, Cristina; Comella Company, Anna; Pujol-Farriols, Ramon; Baños, Josep-Eladi; Galbany-Estragués, Paola; Comella Cayuela, Agustí.  Psychological Distress, Burnout, and Academic Performance in First Year College Students. {\it International Journal of Environmental Research and Public Health}, 19(6), 3356. {\bf Index: JCR: 3.390 (2020): Q1 Public, Environmental and Occupational Health; Q2 Environmental Sciences (2020).  SJR 0.747 Q2 Health, Toxicology and Mutagenesis; Pollution; Public Health, Environmental and Occupational Health. Citations: 0. } \\ DOI: 10.3390/ijerph19063356. \filbreak
\item {\bf 2022}: Marre, Diana; Leinaweaver, Jessaca.  Solidarity exclusions: Problematizing kinship and humanitarianism from the perspective of transnational adoption. {\it American Anthropologist}, , aman.13794. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.1111/aman.13794. \filbreak
\item {\bf 2022}: McIntyre, Lynne; Alvarez, Bruna; Marre, Diana.  “I want to bury it. Will you join me?”: The use of ritual in prenatal loss among women in Catalonia, Spain in the early 21st century. {\it Religions}, 13(4), 336. {\bf Index: SJR 0.256 Q1 Religious Studies. } \\ DOI: https://doi.org/10.3390/rel13040336. \filbreak
\item {\bf 2022}: Ramírez March, Álvaro.  Humanitarian Capture, Solidarity’s Excess: Affect, Experience, and the Mobile Commons in Migrant Solidarity. {\it Antipode}, 54(2), 567-585. {\bf Index: Wiley Online Library. } \\ DOI: 10.1111/anti.12776. \filbreak
\item {\bf 2022}: Ramírez-March, Álvaro; Montenegro, Marisela.  ¿Qué puede la acogida? Aperturas, disputas y críticas en los movimientos sociales por los derechos de las personas migrantes en el Estado español. {\it Quaderns de l'Institut Català d'Antropologia}, 38(1). {\bf Index: } \\ DOI: https://doi.org/10.56247/qua.392. \filbreak
\item {\bf 2022}: Sacré, Hari P.A.; Cawayu, Atamhi; Clemente-Martínez, Chandra Kala.  Adoptees relearning their heritage languages. A postcolonial reading of language and dialogue in transnational adoption. {\it Journal of Adolescent \& Adult Literacy}, {\bf Index: } \\ DOI: 10.1002/jaal.1275. \filbreak
\item {\bf 2022}: Sanmiquel-Molinero, Laura; García-Santesmases, Andrea.  Reseña de "Teoría crip. Signos culturales de lo queer y de la discapacidad". {\it Revista Española de Investigaciones Sociológicas}, 179, 159-166. {\bf Index: SJR 0.292 Q2 Sociology and Political Science. Citations: 1. } \filbreak
\item {\bf 2023}: Alfaro, Karen; Salvo Agoglia, Irene.  “¿Falta cariño en Chile?”.  Discursos sobre el amor y “abandono materno” en las adopciones “irregulares” de niñas y niños pobres en la dictadura militar chilena. {\it Revista del Museo de Antropología, Universidad Nacional de Córdoba, Argentina.}, 16(2), 355–368.. {\bf Index: } \\ DOI: https://doi.org/10.31048/1852.4826.v16.n2.38902. \filbreak
\item {\bf 2023}: Insausti, Santiago Joaquín.  La emergencia de las identidades travestis en la cultura argentina. {\it Kamchatka. Revista de análisis cultural.}, 22, 423-452. {\bf Index: ojs.uv.es. } \\ DOI: 10.7203/KAM.22.26086. \filbreak
\item {\bf 2023}: Insausti, Santiago Joaquín; Ben, Pablo.  Homonationalism, LGBT desaparecidos, and the politics of queer memory in Argentina. {\it Memory Studies}, 16(1), 66-84. {\bf Index: SAGE Journals. } \\ DOI: 10.1177/17506980221140547. \filbreak
\item {\bf 2023}: Insausti, Santiago.  Global Porn Boom and the Latin American Late Cold War: The Case of Perú and Argentina. {\it Journal of Latinoamerican Cultural Studies}, 32(4). {\bf Index: } \filbreak
\item {\bf 2023}: Malgosa, Estel; Alvarez, Bruna; Marre, Diana.  Self-touching, genitals, pleasure and privacy: the governance of sexuality in primary schools in Spain. {\it Sex Education}, , 1-15. {\bf Index: DOI.org (Crossref). } \\ DOI: 10.1080/14681811.2023.2174964. \filbreak
\item {\bf 2023}: Molas, Anna.  Recentering Labor in the Egg Donation Bioeconomy: Egg Donors’ (Re)productive Work and Subjectification in Spain. {\it Medical Anthropology}, , 1-14. {\bf Index: } \\ DOI: 10.1080/01459740.2023.2263806. \filbreak
\item {\bf 2023}: Molas, Anna; Whittaker, Andrea.  Tempting Luck: Temporalities and Risk Anticipation among Egg Donors in Spain. {\it Science, Technology, \& Human Values}, , 01622439231164666. {\bf Index: } \\ DOI: 10.1177/01622439231164666. \filbreak
\item {\bf 2023}: Montenegro, Marisela; Balasch, Marcel; Pujol Tarrés, Joan.  A methodological proposal from situated knowledge epistemology: Narrative productions.. {\it Qualitative Research in Psychology}, 20(4), 542-551. {\bf Index: JCR: 2.228: Impact factor JCR (2020): 2.228, Q2, 94/203 Psychology..  } \\ DOI: https://doi.org/10.1080/14780887.2022.2135278. \filbreak
\item {\bf 2023}: Pujol-Tarrés, Joan.  The methodological and epistemic narrative of narrative productions. {\it Qualitative Research in Psychology}, 20(4), 1-14. {\bf Index: www.tandfonline.com. } \\ DOI: 10.1080/14780887.2023.2183914. \filbreak
\item {\bf 2023}: Ramirez-March, Alvaro; Montenegro, Marisela.  On narrativity, knowledge production, and social change: a diffractive encounter between the Narrative Productions methodology and Participatory Action-Research. {\it Qualitative Research in Psychology}, 20(4), 579-590. {\bf Index: JCR: 2.288: Q2 Psychology, Multidisciplinary.  Citations: 0. } \\ DOI: 10.1080/14780887.2021.1994678. \filbreak
\item {\bf 2023}: Salvo Agoglia, .  Perfect Strangers: Searches and Reunions Between Adult Adoptees And Their Birth Siblings in Chile, Argentina and Spain. {\it Disparidades. Revista de Antropología}, 78(2), e022. {\bf Index: } \\ DOI: https://doi.org/10.3989/dra.2023.022. \filbreak
\item {\bf 2023}: Salvo Agoglia, Irene; LaBrenz, Catherine.  Walking towards Adoption: A Critical Analysis of the PRI Program in Chile.. {\it Adoption Quarterly}, {\bf Index: } \filbreak
\item {\bf 2023}: Salvo Agoglia, Irene; Poveda, David.  ‘No more secrets, it’s over!’: small stories about late adoption disclosure of Chilean adults. {\it Journal of Family Studies}, {\bf Index: } \\ DOI: 10.1080/13229400.2023.2211047. \filbreak
\item {\bf 2023}: Sanmiquel-Molinero, Laura.  Chronotopic diffraction: an analytical device for narrative production methodology applied to ‘adjustment to disability’. {\it Qualitative Research in Psychology}, 20(4), 603-616. {\bf Index: JCR: 4.6: Psychology Multidisciplinary.  SJR 2.63 Q1 Psychology. Citations: 1. } \\ DOI: 10.1080/14780887.2023.2217503. \filbreak
\item {\bf 2023}: Sanmiquel-Molinero, Laura.  The Rehabilitation Hospital as a “Parenthetical Bubble-Shell”: Adjusting to Disability Within the Covid-19 Crisis. {\it Space and Culture}, 26(3), 407-419. {\bf Index: JCR: 1: Q2 Cultural Studies.  SJR 0.482 Q1 Cultural Studies. Citations: 1. } \\ DOI: 10.1177/12063312231181524. \filbreak
\item {\bf 2023}: Sanmiquel-Molinero, Laura; Pujol-Tarrés, Joan; Montenegro, Marisela.  Latin American Perspectives on Parenthood and Disability: Vulnerability, Risk, and Social Inclusion. {\it Social Inclusion}, 11(4), 338-349. {\bf Index: JCR: 1.5: Q3 Social Sciences - Interdisciplinary.  SJR 0.337 Q2 Sociology and Political Science. Citations: 2. } \\ DOI: https://doi.org/10.17645/si.v11i4.7046. \filbreak
\item {\bf 2024}: Desy, Alexandra; Marre, Diana.  The reproductive journeys of French women over 40 seeking assisted reproductive technology treatments in Spain. {\it Social Science \& Medicine}, 351(116951), 1-8. {\bf Index: } \filbreak
\item {\bf 2024}: García-Santesmases, Andrea; Bahner, Julia; Sanmiquel-Molinero, Laura.  A Very Public Private Matter: A Case Study of the Post-Institutional Control of Disabled Sexuality. {\it Sexuality Research and Social Policy}, {\bf Index: JCR: 2.5: Q1 Social Sciences - Interdisciplinary.  SJR 0.874 Q1 Gender Studies. Citations: 0. } \\ DOI: 10.1007/s13178-024-00986-5. \filbreak
\item {\bf 2024}: Insausti, .  La génesis del orgullo queer en la Argentina (1960-1976)”.. {\it Anclajes}, 28(2). {\bf Index: } \filbreak
\item {\bf 2024}: Malgosa, Estel; Alvarez, Bruna; Marre, Diana.  ‘We haven’t even been able to talk!’: Gender norms and masculinity exams in representations of sexuality in Spanish primary schools.. {\it Gender and education}, 36(5), 489–509. {\bf Index: } \\ DOI: http://doi.org/10.1080/09540253.2024.2354857. \filbreak
\item {\bf 2024}: Remorini, Carolina.  With instead of about: Toward an Anthropology that is Critically Integrated into Global Early Childhood Development Interventions. {\it Ethos}, , 1-8. {\bf Index: } \\ DOI: https://doi.org/10.1111/etho.12434. \filbreak
\item {\bf 2024}: Salvo Agoglia, Irene; Gesteira, Soledad.  «Je m’appelle…» : Récits sur les noms propres des personnes adoptées au Chili et en Argentine. {\it Enfances Familles Générations}, 45(online first). {\bf Index: } \filbreak
\end{enumerate} 
% }}}
